---
title: "GenerateReport (Download PDF Files)"
author: "André Calero Valdez"
date: "8/28/2020"
output: html_document
---

This file contains a script to download PDF files if available using the DOI. Only use this script, when you also have legal access to these files.

It takes all RDS output files from the input folder and tries to find a PDF for each DOI.
It only looks for files that are flagged as "selected".

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

# All RDS files in the import folder will be used
folder_import <- "import"

# URL Host for resolving DOI'S
doi_server <- "https://sci-hub.tw/"



file_list <- dir(here::here(folder_import))
for(f in file_list){
dall <- NULL
  dtemp <- read_rds(here::here(folder_import, f))
  dall <- dall %>% bind_rows(dtemp)
}
# Total papers
dall %>% select(TI) %>% unique() %>% count(TI) %>% nrow()


```

## Download of files

First create DOI retrieval links
```{r}
filtered_data <- dall %>% 
  arrange(TI) %>% 
  filter(selected) %>% 
  add_count(TI) %>% filter(n >= 2) %>% 
  mutate(link = paste0(doi_server, DI))
```


Generate IDs and look for first author only to generate file names.
```{r}
selected_data <- filtered_data %>% 
  select(TI, link, DI, n, AU, PY) %>% 
  unique() %>% 
  mutate(id = 1:n()) %>% 
  select(id, link, PY, DI, AU, TI, n) %>% 
  rowwise() %>% 
  separate(AU, "first_author", sep = " ", remove = FALSE, extra = "drop") %>% 
  mutate(fname = paste(formatC(id, width=3, flag="0"), PY, first_author, TI, ".pdf", sep = "_"))

# create a temp file
write_rds(selected_data, "pdfs/selected_data.rds")
```



## Download files
```{r scrape_files}
library(rvest)
get_pdf <- function(html){
      html %>% 
        # The relevant tag
        html_nodes('#buttons') %>%      
        html_nodes("a") %>% 
        html_attr("onclick") %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist() %>% 
        str_remove("location.href='") %>% 
        str_sub(end = -2)# %>% 
        #paste0("https:", .)
  
    }


# remove empty links
links_exist <- selected_data %>% filter(link!=doi_server)
```


```{r scrape_adaptive}

# You can limit "rescraping" by changing 1 to the number of files already there
for(i in 1:nrow(links_exist)) {

  # i <- 14 # debug
  row_data <- links_exist[i, ]
  l <- row_data$link
  tst <- ""
  
  # Can I find the pdf file?
  try({
    print(l)
    tst <- read_html(l) %>% get_pdf()  
  })
  
  try({
    if(!str_starts(tst, "https:")){
      tst <- paste0("https:",tst)
    }
  })
  
  
  # create a name
  fname <- here::here("pdfs", paste0(row_data$fname))
  
  
  # delay 1+N(1,.5) seconds, 
  Sys.sleep(abs(rnorm(n = 1, m = 1, sd = 0.5)+1))
  try({
    download.file(tst, fname, mode="wb")
  })
}

println("Done.")
```

